\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage[greek,english]{babel}
\usepackage[paperheight=6.5in,paperwidth=4.25in,margin=0.5in]{geometry}
\usepackage{multicol}

% Packages

\begin{document}
\begin{flushleft}
\scriptsize
\begin{multicols}{2}
\noindent \textbf{O salutaris Hostia}\newline
Quae caeli pandis ostium:\newline
Bella premunt hostilia,\newline
Da robur, fer auxilium.\newline
\newline
Uni trinoque Domino \newline
Sit sempiterna gloria,\newline
Qui vitam sine termino \newline
Nobis donet in patria.\newline
Amen.\newline

\noindent \textbf{Tantum ergo Sacramentum}\newline
Veneremur cernui:\newline
Et antiquum documentum\newline
Novo cedat ritui:\newline
Praestet fides supplementum\newline
Sensuum defectui.\newline
\newline
Genitori, Genitoque\newline
Laus et iubilatio,\newline
Salus, honor, virtus quoque\newline
Sit et benedictio:\newline
Procedenti ab utroque\newline
Compar sit laudatio.\newline
Amen.\newline     

\textit{P. You have given them bread from heaven}\newline
R. Having all sweetness within it.\newline
\vfill\null
\columnbreak
\textbf{The Divine Praises}\newline
Blessed be God. \newline
Blessed be His Holy Name. \newline
Blessed be Jesus Christ, true God and true Man. \newline
Blessed be the Name of Jesus.\newline
Blessed be His Most Sacred Heart.\newline
Blessed be His Most Precious Blood.\newline
Blessed be Jesus in the Most Holy Sacrament of the Altar.\newline
Blessed be the Holy Spirit, the Paraclete.\newline
Blessed be the great Mother of God, Mary most Holy.\newline
Blessed be her Holy and Immaculate Conception.\newline
Blessed be her Glorious Assumption.\newline
Blessed be the name of Mary, Virgin and Mother.\newline
Blessed be St. Joseph, her most chaste spouse.\newline
Blessed be God in His Angels and in His Saints.\newline
Amen.\newline
\end{multicols}
\textbf{Hymn}\newline
Holy God, we praise thy name;\newline
Lord of all, we bow before thee!\newline
All on earth thy sceptre claim,\newline
All in heav'n above adore thee;\newline
\textit{Infinite, thy vast domain,}\newline
\textit{Everlasting is thy reign. x 2}\newline

Hark! the loud celestial hymn\newline
Angel choirs above are raising;\newline
Cherubim and Seraphim,\newline
In unceasing chorus praising;\newline
\textit{Fill the heav'ns with sweet accord:}\newline
\textit{"Holy, holy, holy Lord!" x 2}\newline
\end{flushleft}
\end{document}